---
title: 'Project 2: R you having fun?'
author: "Eryn Wali (GL), Krisha Vaishnav, Ashita Kumar"
date: "07/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Title 


## Introduction + Research Question 


## Research Hypothesis 
> There is a statistical difference in the way gender and themes are portrayed when female authors who write under male pseudonyms are compared with their female and male author counterparts.


## Corpus Description 


## Summary Paragraph 

```{r}
library(tidyverse)
library(tidytext)
library(pdftools)
library(tidyverse)
library(epubr)
library(scales)
library(ggthemes)

```


```{r}
barnard_txt <- data_frame(text = read_file("BM AM LM P4.txt"),author = "A M Barnard", title = "Behind A Mask, Or A Woman’s Power")
```

```{r}
bell_txt <- data_frame(text = read_file("CB JE P1.txt"),author = "Currer Bell", title = "Jane Eyre")
```

```{r}
dostoevsky_txt <- data_frame(text = read_file("CP FD M1.txt"),author = "Fyodor Dostoevsky", title = "Crime and Punishment")
```

```{r}
sand_txt <- data_frame(text = read_file("DP. GS P3.txt"),author = "George Sand", title = "The Devil's Pool")
```

```{r}
mulock_txt <- data_frame(text = read_file("FB DM F3.txt"),author = "Dinah Maria Mulock", title = "The Fairy Book")
```

```{r}
eliot_txt <- data_frame(text = read_file("M GE P2.txt"),author = "George Eliot", title = "Middlemarch")
```

```{r}
melville_txt <- data_frame(text = read_file("MB HM M4.txt"),author = "Herman Melville", title = "Moby-Dick")
```

```{r}
woolf_txt <- data_frame(text = read_file("MT VW F2.txt"),author = "Virginia Woolf", title = "Monday or Tuesday")
```

```{r}
gaskell_txt <- data_frame(text = read_file("NS EG F1.txt"),author = "Elizabeth Gaskell", title = "North and South")
```

```{r}
austen_txt <- data_frame(text = read_file("PP JA F4.txt"),author = "Jane Austen", title = "Pride and Prejudice")
```

```{r}
dickens_txt <- data_frame(text = read_file("TTC CD M3.txt"),author = "Charles Dickens", title = "A Tale of Two Cities")
```

```{r}
hugo_txt <- data_frame(text = read_file("LM VH M2.txt"),author = "Victor Hugo", title = "Les Misérables")
```


## Sentiment Analysis 


## Named Entity Recognition 

```{r}
install.packages("rJava")
install.packages("openNLP")
install.packages("NLP")
```
```{r echo=TRUE, eval= FALSE, error=FALSE, warning=FALSE, message=FALSE}
install.packages("openNLPmodels.en", dependencies=TRUE, repos = "http://datacube.wu.ac.at/")
```

```{r echo=TRUE, results='hide', message=FALSE}
#NLP Libraries
library(rJava)
library(openNLP)
library(NLP)
```

```{r}
#Tidy data manipulation
library(stringr)
library(tidyr)
library(readr)
library(stringi)
library(textclean)
library(sqldf)
```

```{r}
#Graphics library
library(ggiraphExtra)
library(ggplot2)
library(RColorBrewer)
library(scales)
```

```{r}

```

## Conclusion 


## Reflection 

